Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-02-16 doc/PRF2022/PRF_main.tex
peter added some results in discussion

>>>>

\begin{figure}[t]
\begin{center}
  \includegraphics[height=0.3\textheight]{ChangeLengthForce.pdf}
\end{center}
\begin{caption}{\label{fig:PramChange}
  Panel (a) shows a linear relationship between change of force parameters and the critical shear rate $\dot\gamma^*$. 
  %
  Panel (b) provides numerical results of critical shear rates $\dot\gamma^*$ when the length parameters are adjusted.}
\end{caption}
\end{figure}

%The rheology study has shown that the striated structure under shear and Taylor-Green flows exhibit a shear-thinning behavior.
To further examine the contest between shear and head-tail attraction, we found that a 5\% and 10\% relative increases in the parameters $\gamma$ and
$M$ resulted in 4.29\% and 8.57\% relative increases in critial shear rate $\dot\gamma$, from 0.14 to 0.146 and 0.14 to 0.152, respectively. 
A proportional relationship is observed as the parameters decrease and it is shown in Figure~\ref{fig:PramChange}(a).
Moreover, Figure~\ref{fig:PramChange}(b) shows that 5\% and 10\% decreases in the particle radius c, screening length $\rho$ and repulsion distance $\rho_0$ gave 5.71\%  and 7.14\% increase in $\dot\gamma$ from 0.14 to 0.148 and 0.14 to 0.15.
In addition, 5\% and 10\% increases in length parameters gave 11.43\% and 18.57\% decrease in critical shear rate $\dot\gamma$.
The overall result provides another evidence that a different hydrophobicity suggests a dissimilar rheology and dynamics viscosity from the suspended vesicle experiments.
